---
title: "R Notebook"
output: html_notebook
---

# Question 1.

```{r}
library(ggplot2)
library(CodeClanData)
```

# Question 2. What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
head(backpack)
```


```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight))
```


#Question 3.Are there differences in backpack weight between sex?
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill = sex)) +
  scale_fill_manual(values = c("red", "yellow"))
```


# Question 4-5. What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack) +
  aes(backpack_weight, body_weight, colour = sex) +
  geom_point()
```



# Question 6.What proportion of students report back pain?


```{r}
backpack %>%
  
```


Question 7.

Is this proportion different between men and women?

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

Try both backpack_weight and body_weight as well as the ratio.

Hint: faceting would be useful here.

3 Extensions