---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(readxl)
library(janitor)
```


```{r}
ft_raw <- read_xlsx("raw_data/boing-boing-candy-2015.xlsx")
sxt_raw <- read_xlsx("raw_data/boing-boing-candy-2016.xlsx")
svt_raw <- read_xlsx("raw_data/boing-boing-candy-2017.xlsx")
```

```{r}
names(ft_raw)
```


```{r}
names(ft_raw)
```


```{r}
ft_clean <- ft_raw %>%
  clean_names() %>%
  select(2:96) %>%
  rename("going_out" = "are_you_going_actually_going_trick_or_treating_yourself",
         "age" = "how_old_are_you")

names(ft_clean)
```


```{r}
sxt_clean <- sxt_raw %>%
  clean_names() %>%
  select(2:106) %>%
  
  rename("going_out" = "are_you_going_actually_going_trick_or_treating_yourself", "age" = "how_old_are_you")

names(sxt_clean)
```


```{r}
svt_clean <- svt_raw %>%
  clean_names() %>%
  drop_na() %>%
  select(2:110) %>%
  str_sub(,)
  rename("going_out" = "q1_going_out")

names(svt_clean)
```




```{r}
svt_rname <- rename(svt_jan, "q6_mary_janes" = "q6_anonymous_brown_globs_that_come_in_black_and_orange_wrappers_a_k_a_mary_janes",
       "q6_misc_candy_bar" = "q6_any_full_sized_candy_bar",
       "q6_frestaurant" = "q6_candy_that_is_clearly_just_the_stuff_given_out_for_free_at_restaurants")
names(svt_rname)
```





#1.4.1 Some cleaning hints
You’ll need to combine these three datasets together.
The column country is particularly messy, you will likely need to do some ‘hard coding’ here!

#1.4.2 Analysis questions
What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?

For each of joy, despair and meh, which candy bar revived the most of these ratings?

How many people rated Starburst as despair?

For the next three questions, count despair as -1, joy as +1 and meh as 0.

What was the most popular candy bar by this rating system for each gender in the dataset?
What was the most popular candy bar in each year?
What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?
