---
title: "Rmarkdown reports"
author: "Chris Pettigrew"
date: "28 days later"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Dirty Data Project

## Dataset 2 : Cake Ingredients

Here is my report about my first dataset.  


### Cleaning notes


The dataset I used was `this_one.csv`. To clean it I did the following :

1. Cleaned this...   
2. Cleaned that... 
3. And finally this... 

Here is my code:

```{r, warning=FALSE, message=FALSE}
```

```{r}
library(tidyverse)
library(janitor)
```

```{r}
cakes <- read_csv("raw_data/cake-ingredients-1961.csv")
codes <- read_csv("raw_data/cake_ingredient_code.csv")
```


```{r}
cakes <-
  cakes %>%
  pivot_longer(-Cake, names_to = "code", values_to = "amount") %>%
    left_join(codes) %>%
    drop_na(amount) %>%
    select(-code) %>%
    clean_names()
    
cakes
```

# Which cake has the most cocoa in it?
```{r}
cocoa_max <- cakes %>% filter(ingredient == "Cocoa") %>%
  arrange(desc(amount)) %>%
  head(1)
cocoa_max

```

# For sponge cake, how many cups of ingredients are used in total?
```{r}
sponge_cups <- cakes %>% filter(cake == "Sponge") %>%
                          filter(measure == "cup") %>%
                          summarise(sponge_cups = sum(amount))

```


# How many ingredients are measured in teaspoons?
```{r}
teaspoons <- cakes %>% filter(measure == "teaspoon") %>%
            nrow()
teaspoons
```

# Which cake has the most unique ingredients?
```{r}

n_ingerients <- cakes %>%
  group_by(cake) %>%
  count(n_distinct(ingredient)) %>%
  arrange(desc(n)) %>%
  head(1)

n_ingerients
```

# Which ingredients are used only once?
```{r}


solo_ingredients <- cakes %>%
  group_by(ingredient) %>%
  summarise(n = n()) %>%
  filter(n == 1)

solo_ingredients

```
