---
title: "R Notebook"
output: html_notebook
---

```{r}
temp_in_edinburgh <- c(8L, 7L, 7L, 9L, 8L)
class(temp_in_edinburgh)
````

```{r}
rain_in_edinburgh <- c(10, 20, 20, 60, 20)
class(rain_in_edinburgh)
```

```{r}
cloud_cover_in_edinburgh <- c("partly", "mostly", "mostly", "showers", "partly")
class(cloud_cover_in_edinburgh)
  
```

```{r}
days <- c("Wed", "Thu", "Fri", "Sat", "Sun")
```

```{r}
named_temp_in_edinburgh <- temp_in_edinburgh
names(named_temp_in_edinburgh) <- days
named_temp_in_edinburgh
```

```{r}
named_rain_in_edinburgh <- rain_in_edinburgh
names(named_rain_in_edinburgh) <- days
named_rain_in_edinburgh
```

```{r}
named_cloud_cover_in_edinburgh <- cloud_cover_in_edinburgh
names(named_cloud_cover_in_edinburgh) <- days
named_cloud_cover_in_edinburgh
```

```{r}
mean(temp_in_edinburgh)
```

```{r}
mean(rain_in_edinburgh)
```

```{r}
temp_in_edinburgh[temp_in_edinburgh > 7.8]
#temperature[chance_of_rain <= mean(chance_of_rain)]
```

#Select only the the temperatures when the chance of rain is lower than or equal to the average.
```{r}
temp_in_edinburgh[rain_in_edinburgh <= 26]
```

#Select only the cloud covers from the weekend.
```{r}
cloud_cover_in_edinburgh[4:5]
```


```{r}
test_results <- c(6, 7, 9, 7, 9, 3, 9, 7, 3, 8, 10, 5, 5, 9, 7, 5, 9, 8, 9, 5)
```
#How many marks do we have?
```{r}
length(test_results)
```


#What was the average mark?
```{r}
mean(test_results)
```

#What was the highest and lowest result?
```{r}
max(test_results)
min(test_results)
```

#How many people scored each mark?
```{r}
table(test_results)
```

Express each mark as a percentage out of 100
```{r}
test_results/10 * 100
```


How many people scored eight or higher?

```{r}
sum(test_results >=8)
```

#Matrix
```{r}
temp_forecast_edin <-c (7, 7, 9, 9, 10, 10, 8, 8, 8, 7, 7, 7, 8, 7)
forecast_days <- c("Thu", "Fri", "Sat", "Sun", "Mon", "Tue", "Wed")
week <-c("week 1", "week 2")
```

```{r}
fortnight_temp_forecast <- matrix(temp_forecast_edin, nrow = 2, ncol = 7, byrow = TRUE)
fortnight_temp_forecast
```

```{r}
rownames(fortnight_temp_forecast) <- c("week 1", "week 2")
colnames(fortnight_temp_forecast) <- c("Thu", "Fri", "Sat", "Sun", "Mon", "Tue", "Wed")
fortnight_temp_forecast
```

```{r}
rowMeans(fortnight_temp_forecast)
```

#Find the average temperature on each day of the week (i.e the average temperature on the two Mondays, the two Tuesdays etc.)

```{r}
colMeans(fortnight_temp_forecast)
```

```{r}
fortnight_temp_forecast[2,3]
```

```{r}
fortnight_temp_forecast[2,]
```

```{r}
fortnight_temp_forecast[,"Wed"]
```

```{r}
fortnight_temp_forecast * 1.8 + 32

```

# Factors
Now we will go back to our 5 day forecast.

Make the vector with the days of the week into an ordered factor, where the order correspond to the order of days in a week, starting Monday.

Now select only the temperatures after Tuesday.

```{r}
days_in_order <- c(
  "Monday",
  "Tuesday",
  "Wednesday",
  "Thursday",
  "Friday",
  "Saturday",
  "Sunday"
)

days_of_week_factor <- factor(
  days,
  levels = days_in_order,
  ordered = TRUE
)
```

```{r}
forecast_5_days <- data.frame(
  temp_in_edinburgh = temp_in_edinburgh,
  rain_in_edinburgh = rain_in_edinburgh,
  cloud_cover_in_edinburgh = cloud_cover_in_edinburgh,
  days = days
)
```

```{r}
rm(temp_in_edinburgh)
rm(rain_in_edinburgh)
rm(cloud_cover_in_edinburgh)
rm(days)
rm(days_of_week_factor)
```

```{r}
subset(forecast_5_days, temp_in_edinburgh > mean(temp_in_edinburgh))

```

#Select the rows when the chance of rain is lower than or equal to the average. .
```{r}
subset(forecast_5_days, rain_in_edinburgh <= mean(rain_in_edinburgh))
```

#Sort the data frame so that the highest temperatures come first.
```{r}
positions <- rev(order(forecast_5_days$temp_in_edinburgh))

forecast_5_days[positions, ]
```

```{r}
forecast_5_days_list <- list(
  "Thursday" = as.list(forecast_5_days[1, 1:3]),
  "Friday"   = as.list(forecast_5_days[2, 1:3]),  
  "Saturday" = as.list(forecast_5_days[3, 1:3]),
  "Sunday"   = as.list(forecast_5_days[4, 1:3]),
  "Monday"   = as.list(forecast_5_days[5, 1:3])
)
```

```{r}
forecast_5_days_list$Sunday$rain_in_edinburgh
```

```{r}
forecast_5_days_list$Friday$cloud_cover_in_edinburgh

```

```{r}
forecast_5_days_list$Thursday$temp_in_edinburgh

```

