---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readr)
```


```{r}
state_income <- read.csv("data/state_income_data.csv")
state_income

#state col names by includingfollowing in the script col_names = c("Col name 1")
```

#Read in the cars.csv file and use the col_types() function to ensure you load in:
```{r}
cars <- read_csv("data/cars.csv", col_types = cols(
    X1 = col_character(),
    mpg = col_double(),
    cyl = col_double(),
    disp = col_double(),
    hp = col_double(),
    vs = col_logical()
    )
)

cars
```

#Read in the scotland.txt file using the appropriate function.
```{r}
scotland <- read.csv2("data/scotland.txt", skip = 1)
scotland
```

#How do you read text into a one element character vector?
```{r}

```

#Read in the steam-200k-sample.csv file. Fix any problems you may encounter.
```{r}
steam_200k <- read_csv("data/steam-200k-sample.csv")
```

#Read in the historic_eu_payments.tsv file.

```{r}
eu_payments <- read_tsv("data/historic_eu_payments.tsv")
```

#How do you read lines of text into a multi-element text vector?
```{r}
read_lines()
```

#Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt

```{r}
install.packages("rjson")
library(rjson)
```

```{r}
sample_json_data <- fromJSON(file="http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
sample_json_data

```
