---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(bbplot)
library(CodeClanData)
```

#1 Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
ggplot(qb_revenue_breakdown, aes(fill = Product, y = Revenue, x = Year)) + 
    geom_bar(position="stack", stat="identity") +
    bbc_style() +
  scale_fill_viridis_d(direction = -1) +
  geom_hline(yintercept = 0, size = 1, colour = "#333333") +
  labs(title = "KwikBit Unit1",
       subtitle = "Revenue Breakdown 18/19") +
  theme(legend.position = "top", 
        legend.justification = "left") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))

```


#2Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year. This data is inside qb_monthly_sales, but you will need to use subset.

```{r}
#Done via filter
kb_sales <- qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales")

ggplot(kb_sales, aes(x = Amount, y = Date)) +
  geom_line(colour = "#1380A1", size = 1) +
  bbc_style() +
  labs(title="Product Category Leader",
       subtitle = "Kwikbit Unit 1 Sales 18/19")

#Done via subset then removing all of the elements
ggplot(subset(qb_monthly_sales, Cashflow == "Kwikbit Unit 1 Sales"), 
       aes(x = Amount, y = Date)) +
  geom_line(colour = "#1380A1", size = 1) +
  bbc_style() +
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank()) 

```

#3Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.
```{r}
rc_line <- qb_monthly_sales %>%
  filter(Cashflow == "Cost" | Cashflow == "Total Revenue")

ggplot(rc_line, aes(x = Date, y = Amount, colour = Cashflow)) +
  geom_line(size = 1) +
  geom_hline(yintercept = 0, size = 1, colour="#333333") +
  scale_colour_manual(values = c("#FAAB18", "#1380A1")) +
  bbc_style() +
  labs(title="Revenue and Cost",
       subtitle = "100% Growth in 12 Months") +
  theme(
  axis.ticks.x = element_line(colour = "#333333"), 
  axis.ticks.length =  unit(0.26, "cm"))

```


#4Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.
```{r}
ggplot(qb_competitors, aes(x = Year, y = Revenue, fill = Company)) +
geom_area() +
  scale_fill_manual(values = c("#FAAB18", "#1380A1","#990000", "#588300")) +
  bbc_style() +
  geom_hline(yintercept = 0, size = 1, colour = "#333333") +
  labs(title = "Rapid category growth",
       subtitle = "Growth by competitor") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))
```


#5Now show the sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.
```{r}
ggplot(qb_competitors) +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_line(colour = "#1380A1", size = 1) +
  geom_point(
    aes(x = Year, y = Revenue, fill = Company)) +
  bbc_style() +
  labs(title = "Rapid category growth",
       subtitle = "Growth by competitor") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE))

```

#6Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between individuals and people. Data is in qb_device_data.

```{r}
qb_device_data
```


```{r}

ggplot(qb_device_data) +
  aes(x = hours, y = counts, fill = device) +
  geom_line(colour = "#1380A1", size = 1) +
   facet_wrap(~ device, ncol = 4)
```



```{r}
qb_device_data
```

